Manuscript for MADA Project

### 2023-04-24 code/analysis_code/exploratory_analysis/exploratory_analysis.Rmd
Additional Updates to MADA Project

```{r}
# Recoding hispanic_status for the figure
data_clean_main1 <- data_clean_main
data_clean_main1$hispanic_status <- recode_factor(data_clean_main1$hispanic_status, '1' = 'Non-hispanic Female', '2' = 'Hispanic Female')

# Summarizing mammogram_status and Hispanic_status in the given years
figure1 <- ggplot(data_clean_main1, aes(x = mammogram_status))+
  geom_bar(aes(fill = hispanic_status), stat = "count", color = "white",
    position = position_dodge(0.9)) +
  facet_wrap(~year) +
  scale_x_discrete(labels = c("No", "Yes")) +
  scale_y_continuous(breaks = c(1000, 2000, 3000, 4000, 5000, 6000))
figure1

# Saving this figure
ggsave(filename = here("results", "exploratory_analysis_result", "figure1_mammogram_ses.png"), plot = figure1)
```

>>>>

```{r}
# Recoding hispanic_status for the figure
data_clean_main1 <- data_clean_main
data_clean_main1$hispanic_status <- recode_factor(data_clean_main1$hispanic_status, '1' = 'Non-hispanic', '2' = 'Hispanic')

# Summarizing mammogram_status and Hispanic_status in the given years
figure1 <- ggplot(data_clean_main1, aes(x = mammogram_status)) +
  geom_bar(aes(fill = hispanic_status), stat = "count", color = "white",
    position = position_dodge(0.9)) +
  facet_wrap(~year) +
  scale_x_discrete(labels = c("No", "Yes")) +
  scale_y_continuous(breaks = c(1000, 2000, 3000, 4000, 5000, 6000)) +
  theme(legend.position = "bottom", 
        legend.title = element_text(size = 12))

figure1

# Saving this figure
ggsave(filename = here("results", "exploratory_analysis_result", "figure1_mammogram_ses.png"), plot = figure1, dpi = 300)
```

### 2023-04-24 code/analysis_code/statistical_analysis/1_model_fitting/model_fitting.Rmd
Additional Updates to MADA Project

# Making sure there are no missing values in any variables
any(is.na(data_clean_main))
```

@@

# Looking at the summary of log_fit_year
tidy(log_fit_year)
```

@@

# Looking at the summary of log_fit_hispanicstatus
tidy(log_fit_hispanicstatus)
exp(-0.5624346)
```

@@

# Looking at the summary of log_fit_age
tidy(log_fit_age)
```

@@

# Looking at the summary of log_fit_income
tidy(log_fit_income)
```

@@

# Looking at the summary of log_fit_education
tidy(log_fit_education)
```

@@

# Looking at the summary of log_fit_maritalstatus
tidy(log_fit_maritalstatus)
```

@@

# Looking at the summary of log_fit_regionresidence
tidy(log_fit_regionresidence)
```

@@

# Looking at the summary of log_fit_insurancestatus
tidy(log_fit_insurancestatus)
```

@@

# Looking at the summary of log_fit_healthstatus
tidy(log_fit_healthstatus)
```

@@

# Looking at the summary of log_fit_usualmedicalcarestatus
tidy(log_fit_usualmedicalcarestatus)
```

@@

# Looking at the summary of log_fit_smokingstatus
tidy(log_fit_smokingstatus)
```

@@

# Looking at the summary of log_fit_alcoholstatus
tidy(log_fit_alcoholstatus)
```

@@

# Looking at the summary of log_fit_diabetesstatus
tidy(log_fit_diabetesstatus)
```

>>>>

# Making sure there are no missing values in any variables
any(is.na(data_clean_main))

# Lets convert the variables to factor variables just to make sure that they are not treated as continuous variables in our analysis
data_clean_main$age <- as.factor(data_clean_main$age)
data_clean_main$hispanic_status <- as.factor(data_clean_main$hispanic_status)
data_clean_main$income <- as.factor(data_clean_main$income)
data_clean_main$education <- as.factor(data_clean_main$education)
data_clean_main$marital_status <- as.factor(data_clean_main$marital_status)
data_clean_main$region_residence <- as.factor(data_clean_main$region_residence)
data_clean_main$insurance_status <- as.factor(data_clean_main$insurance_status)
data_clean_main$privateinsurance_status <- as.factor(data_clean_main$privateinsurance_status)
data_clean_main$medicaid_status <- as.factor(data_clean_main$medicaid_status)
data_clean_main$medicare_status <- as.factor(data_clean_main$medicare_status)
data_clean_main$health_status <- as.factor(data_clean_main$health_status)
data_clean_main$mammogram_status <- as.factor(data_clean_main$mammogram_status)
data_clean_main$usual_medicalcare_status <- as.factor(data_clean_main$usual_medicalcare_status)
data_clean_main$smoking_status <- as.factor(data_clean_main$smoking_status)
data_clean_main$alcohol_status <- as.factor(data_clean_main$alcohol_status)
data_clean_main$diabetes_status <- as.factor(data_clean_main$diabetes_status)

# Recoding the variables
data_clean_main$hispanic_status <- recode_factor(data_clean_main$hispanic_status, '1' = 'Non-Hispanic', '2' = 'Hispanic')
data_clean_main$mammogram_status <- recode_factor(data_clean_main$mammogram_status, '0' = 'No', '1' = 'Yes')
data_clean_main$age <- recode_factor(data_clean_main$age, '1' = '40-44 years', '2' = '45-49 years', '3' = '50-54 years', '4' = '55-59 years', '5' = '60-64 years', '6' = '65-69 years', '7' = '70-74 years')
data_clean_main$income <- recode_factor(data_clean_main$income, '1' = 'At or above poverty threshold', '2' = 'Below poverty threshold')
data_clean_main$education <- recode_factor(data_clean_main$education, '1' = 'Never attended/kindergarten only', '2' = 'Less than high school', '3' = 'High school', '4' = 'Some college or Associate degree', '5' = 'Bachelor degree and higher')
data_clean_main$marital_status <- recode_factor(data_clean_main$marital_status, '0' = 'Never married', '1' = 'Married', '2' = 'Single (separated/widowed/divorced)', '3' = 'Living with partner')
data_clean_main$region_residence <- recode_factor(data_clean_main$region_residence, '1' = 'Northeast', '2' = 'North Central/Midwest', '3' = 'South', '4' = 'West')
data_clean_main$insurance_status <- recode_factor(data_clean_main$insurance_status, '0' = 'No Coverage', '1' = 'Coverage')
data_clean_main$health_status <- recode_factor(data_clean_main$health_status, '1' = 'Excellent/very good/good', '2' = 'Fair/poor')
data_clean_main$usual_medicalcare_status <- recode_factor(data_clean_main$usual_medicalcare_status, '0' = 'No place', '1' = 'Usual place')
data_clean_main$smoking_status <- recode_factor(data_clean_main$smoking_status, '0' = 'Never', '1' = 'Current', '2' = 'Former')
data_clean_main$alcohol_status <- recode_factor(data_clean_main$alcohol_status, '0' = 'Never', '1' = 'Current', '2' = 'Former')
data_clean_main$diabetes_status <- recode_factor(data_clean_main$diabetes_status, '0' = 'No', '1' = 'Yes')
```

@@

# Looking at the summary of log_fit_year
bivariate_year <- tidy(log_fit_year)
saveRDS(bivariate_year, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_year.rds")))
```

@@

# Looking and saving the summary of log_fit_hispanicstatus
bivariate_hispanic <- tidy(log_fit_hispanicstatus)
saveRDS(bivariate_hispanic, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_hispanic.rds")))
```

@@

# Looking at the summary of log_fit_age
tidy(log_fit_age)
bivariate_age <- tidy(log_fit_age)
saveRDS(bivariate_age, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_age.rds")))
```

@@

# Looking at the summary of log_fit_income
tidy(log_fit_income)
bivariate_income <- tidy(log_fit_income)
saveRDS(bivariate_income, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_income.rds")))
```

@@

# Looking at the summary of log_fit_education
tidy(log_fit_education)
bivariate_education <- tidy(log_fit_education)
saveRDS(bivariate_education, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_education.rds")))
```

@@

# Looking at the summary of log_fit_maritalstatus
tidy(log_fit_maritalstatus)
bivariate_maritalstatus <- tidy(log_fit_maritalstatus)
saveRDS(bivariate_maritalstatus, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_maritalstatus.rds")))
```

@@

# Looking at the summary of log_fit_regionresidence
tidy(log_fit_regionresidence)
bivariate_regionresidence <- tidy(log_fit_regionresidence)
saveRDS(bivariate_regionresidence, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_regionresidence.rds")))
```

@@

# Looking at the summary of log_fit_insurancestatus
tidy(log_fit_insurancestatus)
bivariate_insurancestatus <- tidy(log_fit_insurancestatus)
saveRDS(bivariate_insurancestatus, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_insurancestatus.rds")))
```

@@

# Looking at the summary of log_fit_healthstatus
tidy(log_fit_healthstatus)
bivariate_healthstatus <- tidy(log_fit_healthstatus)
saveRDS(bivariate_healthstatus, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_healthstatus.rds")))
```

@@

# Looking at the summary of log_fit_usualmedicalcarestatus
tidy(log_fit_usualmedicalcarestatus)
bivariate_usualmedicalcarestatus <- tidy(log_fit_usualmedicalcarestatus)
saveRDS(bivariate_usualmedicalcarestatus, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_usualmedicalcarestatus.rds")))
```

@@

# Looking at the summary of log_fit_smokingstatus
tidy(log_fit_smokingstatus)
bivariate_smokingstatus <- tidy(log_fit_smokingstatus)
saveRDS(bivariate_smokingstatus, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_smokingstatus.rds")))
```

@@

# Looking at the summary of log_fit_alcoholstatus
tidy(log_fit_alcoholstatus)
bivariate_alcoholstatus <- tidy(log_fit_alcoholstatus)
saveRDS(bivariate_alcoholstatus, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_alcoholstatus.rds")))
```

@@

# Looking at the summary of log_fit_diabetesstatus
tidy(log_fit_diabetesstatus)
bivariate_diabetesstatus <- tidy(log_fit_diabetesstatus)
saveRDS(bivariate_diabetesstatus, file = (here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_diabetesstatus.rds")))
```

### 2023-04-24 code/analysis_code/statistical_analysis/2_model_evaluation/model_evaluation.Rmd
MADA Project Additional Update
Additional Updates to MADA Project

```{r, warning = FALSE, message = FALSE}
# Loading required packages
library(readr)
library(tidyverse)
library(dplyr)
library(gtsummary)
library(ggplot2)
library(ggthemes)
library(here)
library(tidymodels)
library(performance)
library(vip)
library(broom)
```

@@

# Using roc_auc() for estimating the area under the curve 
data_clean_main_aug %>% 
  roc_auc(truth = mammogram_status, .pred_0)

```

@@

# Using roc_auc() for estimating the area under the curve 
data_clean_main_aug2 %>% 
  roc_auc(truth = mammogram_status, .pred_0)
```

>>>>

```{r, warning = FALSE, message = FALSE}
# Loading required packages
library(readr)
library(tidyverse)
library(dplyr)
library(gtsummary)
library(ggplot2)
library(ggthemes)
library(here)
library(tidymodels)
library(performance)
library(vip)
library(broom)
library(gridExtra)
library(cowplot)
```

@@

# Using roc_auc() for estimating the area under the curve 
data_clean_main_aug %>% 
  roc_auc(truth = mammogram_status, .pred_0)
```

@@

# Using roc_auc() for estimating the area under the curve 
data_clean_main_aug2 %>% 
  roc_auc(truth = mammogram_status, .pred_0)

# Combining and saving the above 2 ROC curves for full model and alternative model
roc_combined <- plot_grid(roc_fullmodel, roc_altmodel, ncol = 2, align = "h", axis = "tb",
                           labels = c("ROC Curve for the full model", "ROC Curve for the alternative model"),
                           label_size = 10)
roc_combined
ggsave(filename = here("results", "statistical_analysis_result", "2_model_evaluation_result", "figure4_roc_combined.png"), plot = roc_combined)
```

### 2023-04-24 code/analysis_code/statistical_analysis/3_machine_learning/machine_learning.Rmd
Additional Updates to MADA Project

# Plotting and saving the final fit
plot_lasso <- extract_fit_engine(final_lasso_fit)
lasso_model_figure <- plot(plot_lasso, "lambda")
lasso_model_figure
ggsave(filename = here("results","statistical_analysis_result", "3_machine_learning_result", "figure3_lasso_model.png"), plot = lasso_model_figure)

>>>>

# Plotting the final fit
plot_lasso <- extract_fit_engine(final_lasso_fit)
lasso_model_figure <- plot(plot_lasso, "lambda")
lasso_model_figure

### 2023-04-24 products/manuscript/Manuscript.qmd
Additional Updates to MADA Project

---
title: "Manuscript for MADA Project"
subtitle: "Trend in mammogram screening for breast cancer and socio-economic status of hispanic and non-hispanic women during 2000, 2005, 2010, and 2015"
author: Shiwani Sapkota
date: "`r Sys.Date()`"
bibliography: citations.bib
csl: jama.csl
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
---

# 1. Summary/Abstract

@@

# 2. Introduction

@@

# 3. Methods

@@

# 4. Results

# 4.1. Exploratory/Descriptive analysis

Table 1 shows the demographic characteristics of the study population on the basis of mammogram screening status. Out of 24,848 subjects, there were 21,466 (86.4%) women doing mammogram screening while there were 3,382 (13.6%) women who did not do mammogram screening. Similarly, there were 21,056 (84.7%) non-Hispanic women and 3,792 (15.3%) Hispanic women. Larger proportion of women aged 40-44 years did not  go for mammogram screening compared to other aged women. Similarly, women with education level of some college or associate degree had higher proportion of mammogram screening. Majority of our participants (58.7%) were never smokers. Out of 21,056 non-Hispanic women, 18,432 (87.6%) had mammogram screening while out of 3,792 Hispanic women, 3,034 (80%) had mammogram screening. Figure 1 shows increasing trend in mammogram screening among women going through 2000 to 2015.

**Table 1: Demographic characteristics of study population**
```{r warning = FALSE, message = FALSE}
#| echo: FALSE
library(here)
library(knitr)

# Loading the `demographic_table1.rds` table which was created during the data exploratory process

result_table1 <- readRDS(here("results", "exploratory_analysis_result", "demographic_table1.rds"))
result_table1 
```

```{r}
#| label: Figure 1
#| fig-cap: "Summary of mammography screening status and the Hispanic status of study population in 2000, 2005, 2010, and 2015."
#| echo: FALSE

# Loading the `figure1_mammogram_ses.png` figure which was created during the data exploratory process
include_graphics(here("results", "exploratory_analysis_result", "figure1_mammogram_ses.png"))
```
**Figure 1: Summary of mammography screening status and the Hispanic status of study population in 2000, 2005, 2010, and 2015**

# 4.2. Statistical Analysis
# 4.2.1. Model Fitting

We aimed to explore the bivariate and multivariate relationship between mammogram screening and other hypothesized predictors i.e., year, hispanic status, age, income, education, marital status, region of residence, insurance status, health status, usual medical care status, smoking status, alcohol status, and diabetes status. Logistic regression was used for examining such relationships. In bivariate relationship (Table 2), we found statistically significant relationship between mammogram screening and hispanic status of women and found the log odds of having mammogram screening for Hispanic women as -0.56 compared to non-Hispanic women. The log odds of having mammogram was found as 0.25 in year 2015 compared to that of 2000. We also found that the log odds of having mammogram increased with age, and education. We found the log odds of having mammogram screening for women with income below the poverty threshold as -0.76 compared to women with income at or above the poverty threshold. The log odds of having mammogram for married was 0.67 compared to never married women. Women having the usual medical place had the log odds of having mammogram of 1.47 compared to those having no usual medical place. ***add bivariate relation table 2. Similarly, Table 3 shows the multivariate relationship between mammogram screening and all other predictors of interests. All predictors of interests were found to be significant predictors of mammogram.

Table 4 shows the model performance comparison which compared the models' performance including various numbers of predictors. The best model performance was found for the full model including all predictors of interests (AIC: 16981 and RMSE: 0.32). Similarly, based on model performance comparison, second best model was identified as the model including demographic predictors (age, hispanic status, income, education, marital status, and region of residence) that had AIC of 17764.1 and RMSE of 0.33.

**Table 3: Full model fitting using mammogram_status as outcome variable and other variables as predictor variables.**
```{r, warning = FALSE, message = FALSE}
#| echo: FALSE

# Loading the `full_model.rds` table which was created during the model fitting analysis process
result_table2 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "full_model.rds"))
print(result_table2, n = Inf, width = Inf)
```

**Table 4: Model Performance Comparisons.**
```{r, warning = FALSE, message = FALSE}
#| echo: FALSE

# Loading the `model_performance_comparison.rds` table which was created during the model fitting analysis process
result_table4 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "model_performance_comparison.rds"))
print(result_table4)
```

# 4.2.2. Model Evaluation

Model evaluation was performed for the full model including all predictors of interest and the alternative model including only hispanic status of women as the main predictor for mammogram. Data splitting was done by putting 3/4 of the data into the training set and recipe was created accordingly for fitting the full and alternative logistic models. Figure 2 shows the ROC curve for the full model (using mammogram status as the main outcome of interest and other variables as predictors) having ROC-AUC as 0.76 while Figure 3 shows the ROC curve for the alternative model (using mammogram status as the main outcome of interest and hispanic status as the main predictor) having ROC-AUC as 0.54. The larger the area under the curve, better the model is at distinguishing those with the outcomes from those without the outcomes. Hence, from the given 2 figures, we can say that for mammogram status, the full model with all the predictors of interest is better than the alternative model having only Hispanic status as the main predictor.

```{r}
#| label: Figure 2
#| fig-cap: "ROC Curve for the full model."
#| echo: FALSE

# Loading the `figure2_roc_fullmodel.png` figure which was created during the model evaluation process
include_graphics(here("results", "statistical_analysis_result", "2_model_evaluation_result", "figure2_roc_fullmodel.png"))
```
**Figure 2: ROC Curve for the full model**

```{r}
#| label: Figure 3
#| fig-cap: "ROC Curve for the alternative model."
#| echo: FALSE

# Loading the `figure3_roc_altmodel.png` figure which was created during the model evaluation process
include_graphics(here("results", "statistical_analysis_result", "2_model_evaluation_result", "figure3_roc_altmodel.png"))
```
**Figure 3: ROC Curve for the alternative model**

# 4.2.3. Machine Learning

@@

**Table 4: Model Selection using Null method, Decision tree method, and Lasso method.**
```{r, warning = FALSE, message = FALSE}
#| echo: FALSE

# Loading the `machinelearning_results.rds` table which was created during the machine learning analysis process
result_table3 <- readRDS(here("results", "statistical_analysis_result", "3_machine_learning_result", "machinelearning_results.rds"))
print(result_table3)
```

# 5. Discussion

@@

# 6. Conclusions

@@

# 7. References

>>>>

---
title: "Manuscript for MADA Project"
subtitle: "Trend in mammogram screening for breast cancer and socio-economic status of hispanic and non-hispanic women during 2000, 2005, 2010, and 2015"
author: Shiwani Sapkota
date: "`r Sys.Date()`"
bibliography: citations.bib
csl: jama.csl
prefer-html: true
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# load R packages
library(here) 
library(knitr)
library(ggplot2)
library(dplyr)
library(plotly)
library(gt)
library(skimr) 
library(ggpubr)
library(kableExtra)
library(gridExtra)
```

# Summary/Abstract

@@

# Introduction

@@

# Methods

@@

# Results

## Exploratory/Descriptive analysis

Table 1 shows the demographic characteristics of the study population on the basis of mammogram screening status (Yes/No). Out of 24,848 subjects, there were 21,466 (86.4%) women doing mammogram screening while there were 3,382 (13.6%) women who did not do mammogram screening. Similarly, there were 21,056 (84.7%) non-Hispanic women and 3,792 (15.3%) Hispanic women. Larger proportion of women aged 40-44 years did not  go for mammogram screening compared to other aged women. Similarly, women with education level of some college or associate degree had higher proportion of mammogram screening. Majority of our participants (58.7%) were never smokers. Out of 21,056 non-Hispanic women, 18,432 (87.6%) had mammogram screening while out of 3,792 Hispanic women, 3,034 (80%) had mammogram screening. Figure 1 shows increasing trend in mammogram screening among women going through 2000 to 2015.

**Table 1: Demographic characteristics of study population by mammogram screening status**
```{r, message = FALSE}
#| echo: FALSE

# Loading the `demographic_table1.rds` table which was created during the data exploratory process
result_table1 <- readRDS(here("results", "exploratory_analysis_result", "demographic_table1.rds"))
result_table1
```

```{r}
#| echo: FALSE

# Loading the `figure1_mammogram_ses.png` figure which was created during the data exploratory process
knitr::include_graphics(here("results", "exploratory_analysis_result", "figure1_mammogram_ses.png"))
```
**Figure 1: Summary of mammography screening status and the Hispanic status of study population in 2000, 2005, 2010, and 2015.**

## Statistical Analysis
### Model Fitting

We aimed to explore the bivariate and multivariate relationship between mammogram screening and other hypothesized predictors i.e., year, hispanic status, age, income, education, marital status, region of residence, insurance status, health status, usual medical care status, smoking status, alcohol status, and diabetes status. Logistic regression was used for examining such relationships. In bivariate relationship (Supplementary Tables 3-12), we found statistically significant relationship between mammogram screening and hispanic status of women and found the log odds of having mammogram screening for Hispanic women as -0.56 compared to non-Hispanic women. The log odds of having mammogram was found as 0.25 in year 2015 compared to that of 2000. We also found that the log odds of having mammogram increased with age, and education. We found the log odds of having mammogram screening for women with income below the poverty threshold as -0.76 compared to women with income at or above the poverty threshold. The log odds of having mammogram for married was 0.67 compared to never married women. Women having the usual medical place had the log odds of having mammogram of 1.47 compared to those having no usual medical place. Similarly, Table 2 shows the multivariate relationship between mammogram screening and all other predictors of interests. All predictors of interests were found to be significant predictors of mammogram.

Table 3 shows the model performance comparison which compared the models' performance including various numbers of predictors. The best model performance was found for the full model including all predictors of interests (AIC: 16981 and RMSE: 0.32). Similarly, based on model performance comparison, second best model was identified as the model including demographic predictors (age, hispanic status, income, education, marital status, and region of residence) that had AIC of 17764.1 and RMSE of 0.33.

**Table 2: Full model fitting using mammogram_status as outcome variable and other variables as predictor variables.**
```{r, warning = FALSE, message = FALSE}
#| echo: FALSE

# Loading the `full_model.rds` table which was created during the model fitting analysis process
result_table2 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "full_model.rds"))
kable(result_table2 %>% mutate(term = gsub("as\\.factor", "", term)),  align = "c", format.args = list(digits = 3)) %>%
  row_spec(row = 0, color = "white") %>% kable_styling(full_width = T, bootstrap_options = "striped", font_size = 10)
```

**Table 3: Model Performance Comparisons.**
```{r, warning = FALSE, message = FALSE}
#| echo: FALSE

# Loading the `model_performance_comparison.rds` table which was created during the model fitting analysis process
result_table3 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "model_performance_comparison.rds"))
kable(result_table3 %>% select(Name, AIC, BIC, RMSE),  align = "c", format.args = list(digits = 3)) %>%
  row_spec(row = 0, color = "white") %>% kable_styling(full_width = T, bootstrap_options = "striped", font_size = 10)
```

### Model Evaluation

Model evaluation was performed for the full model including all predictors of interest and the alternative model including only hispanic status of women as the main predictor for mammogram. Data splitting was done by putting 3/4 of the data into the training set and recipe was created accordingly for fitting the full and alternative logistic models. Figure 2 shows the ROC curve for the full model (using mammogram status as the main outcome of interest and other variables as predictors) having ROC-AUC as 0.76 and the ROC curve for the alternative model (using mammogram status as the main outcome of interest and hispanic status as the main predictor) having ROC-AUC as 0.54. The larger the area under the curve, better the model is at distinguishing those with the outcomes from those without the outcomes. Hence, from the given figure, we can say that for mammogram status, the full model with all the predictors of interest is better than the alternative model having only Hispanic status as the main predictor.

```{r}
#| label: Figure 2
#| echo: FALSE

# Loading the `"figure4_roc_combined.png"l.png` figure which was created during the model evaluation process
include_graphics(here("results", "statistical_analysis_result", "2_model_evaluation_result", "figure4_roc_combined.png"))
```

**Figure 3: ROC Curve for the full model and alternative model.**

### Machine Learning

@@

**Table 4: Model Selection using Null method, Decision tree method, and Lasso method.**
```{r, warning = FALSE, out.width = "100%", message = FALSE}
#| echo: FALSE

# Loading the `machinelearning_results.rds` table which was created during the machine learning analysis process
result_table4 <- readRDS(here("results", "statistical_analysis_result", "3_machine_learning_result", "machinelearning_results.rds"))
kable(result_table4 %>% select(Model, ROC_AUC),  align = "c") %>%
  row_spec(row = 0, color = "white") %>% kable_styling(full_width = T, bootstrap_options = "striped", font_size = 14, position = "center")
```

# Discussion

@@

# Conclusions

@@

# References
